### 2016-11-08 src/4_OnlineLearning.tex
fixing learning alg definition

A learning algorithm $\mathcal{A}$ takes as input a data set $S \in \mathcal{S}$ and outputs a function $f$:

@@

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, is the space of functions that the algorithm is allowed to search. The selection of $f_S$ is based on the minimization if the expected risk of the loss function $V(f(x),y): \R\times\R\to\R$.

\begin{equation}
\label{eq:expetedrisk}
E[V(f(x),y)] = \int_{X \times Y} V(f(x),y) \, \, dp(x,y)
\end{equation}

>>>>

A learning algorithm $\mathcal{A}$ takes as input a data set $S \in \mathscr{T}$ and selects from $\mathcal{H}$ a function $f$ such that $f(x)\approx y $ in a predictive way:

@@

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, is the space of functions that the algorithm is allowed to search. The selection of $f$ is based on the minimization of the expected error of the loss function $V(f(x),y)$ defined as:

\begin{eqnarray*}
 V: Y\times Y &\rightarrow & Y \\
f(x), y &\rightarrow &V(f(x),y)
\end{eqnarray*}

Therefore, given a function $f$ a loss function $V$ and a probability distribution $p$ over $X \times Y$, the expected error of $f$ is:

\begin{equation}
\label{eq:expetedrisk}
I[f] = E[V(f(x),y)] = \int_{X \times Y} V(f(x),y) \; dp(x,y)
\end{equation}
